\chapter{Background}
\section{Motivation} % (fold)
\label{sec:motivation}

Seeking for places to eat is a thing in my genuine. I always want to keep track of my food adventures so that next time I could have better sense of what kind of courses I should order. I could also give recommendations to my friends about the adventures. Luckily, it turns out that I am not the only one want to do such kind of thing. A few of my friends tells that people nowadays love to take photos of the food before they eat, and post their photos to all kinds of social media such as Facebook, Twitter, Weibo (Chinese Twitter) etc.. Especially asian students have really strong motivation to take pictures of food when they eat. \\

After searching the apps available in apple app store, I didn't find any suitable choice for my need. So I came up with an idea that I need to make best use of skills and build a good app for people who like to explore food world with friends. 
\newpage

% section motivation (end)
\section{Restaurants Review Apps} % (fold)
\label{sec:current_review_apps}

\subsection{Yelp} % (fold)
\label{sub:yelp}

Yelp is used by tremendous people to get rate of restaurants in order to pick a place to eat. The searching filter for Yelp app is really good since they have a very rich database of different kinds of restaurants as well as different reviews from many people. The app provide a way to check with map and give direction the restaurant which is helpful for people to find the place. On the other hand, since they have a really large database, it is not easy to find what exactly you want to go. And most of the reviews are from people you don't know, it is highly possible that the taste of the people might be different from yours. Let alone there are people paid to make fake good reviews or bad reviews for some restaurants. \\

In this app, you're not using this looking for suggestions of where you're going to eat, but you need to get suggestions from your social media where your friends published restaurants reviews. In this way, fake reviews will be avoided. \\
% subsection yelp (end)
\newpage
% section current_review_apps (end)
\section{Recipe Related Apps} % (fold)
\label{awx:receipe_related_apps}
%some text\cite{citation-1-name-here}, some more text
\subsection{Evernote Food} % (fold)
\label{sub:evernote_food}

Food app from Evernote did a good job showing the meals. The user interface is really friendly. Adding tags to the meal is easy and choosing place information is convenient in Food.  The app also provided functionality to add a cuisine recipe as well. But people likes to take pictures of their food not always into making food. So in our project, we won't do any recipe recording.

% subsection evernote_food (end)
% section receipe_related_apps (end)




